### 2009-11-27 doc/tech_doc/client/job_description_mapping.tex
Updating job description mapping document.

\subsubsubsection{DownloadToCache}
\begin{inouttabular}
XRSL & \todo{} & \todo{}\\
ARC-JSDL & DataStaging/File/DownloadToCache & DataStaging/File/DownloadToCache\\
\end{inouttabular}

@@

\section{XRSL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CTC}
\toprule
\NST{XRSL input} & \NST{Internal representaion} & \NST{XRSL output}\\
\midrule
\defineheadfoot
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles& DataStaging.File.Name,\linebreak DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & \TODO & \TODO \\
outputFiles & DataStaging.File.Name,\linebreak DataStaging.File.Target & outputFiles \\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Resources.TotalCPUTime & \NM \\
benchmarks & Resources.TotalCPUTime & \NM \\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout, outputFiles\\
stderr & Application.Error & stderr, outputFiles\\
join & Application.Join & \NM\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads,\linebreak DataStaging.File.Target.Threads & \NM\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & \NM\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & \NM\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & \NM & \NM\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & \NM\\
dryRun & \NM & \NM\\
rsl\_substitution & \NST{Processed internally by the parser} & \NM\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabularx}
\end{center}

>>>>

\subsubsubsection{DownloadToCache}
\begin{inouttabular}
XRSL & cache & \NST{cache in URL-option}\\
ARC-JSDL & DataStaging/File/DownloadToCache & DataStaging/File/DownloadToCache\\
\end{inouttabular}

@@

\section{XRSL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CTC}
\toprule
\NST{XRSL input} & \NST{Internal representaion} & \NST{XRSL output}\\
\midrule
\defineheadfoot
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles& DataStaging.File.Name,\linebreak DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & DataStaging.File.DownloadToCache & \NST{cache in URL-option} \\
outputFiles & DataStaging.File.Name,\linebreak DataStaging.File.Target & outputFiles \\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Resources.TotalCPUTime & \NM \\
benchmarks & Resources.TotalCPUTime & \NM \\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout, outputFiles\\
stderr & Application.Error & stderr, outputFiles\\
join & Application.Join & \NM\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads,\linebreak DataStaging.File.Target.Threads & \NM\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & \NM\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & \NM\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & \NM & \NM\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & \NM\\
dryRun & \NM & \NM\\
rsl\_substitution & \NST{Processed internally by the parser} & \NM\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabularx}
\end{center}
